### 2013-12-17 research/paper/figure/velocity_compare.tex
corrected some stuff uploaded 11.01 PM Malaysia

\begin{figure}
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(1,0.3)(0,0.8)
    % % %90
    \put(0.025,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_60_0.075.eps}}
    \put(0.495,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_165_0.175.eps}}

@@

  \caption{Time histories of velocity at two different $\zeta$ and $U^*$ which produce the same mean power ($1.2\times10^{-3}$). Data presented in (a) are at $\ustar=60$, $\zeta=0.075$ and (b) are at $\ustar=165$, $\zeta=0.175$. Both data sets were obtained using Quasi-steady state assumption using input $C_y$ parameters at $Re=165$. Shedding is evident in both signals as a high frequency fluctuation but the amplitude of the slower fluctuations remains constant in both cases. \JL{KASUN: The different scale on the x-axes make these two plots difficult to compare. I think a more powerful comparison can be made by keeping the x-scale the same (include more periods of the case at $U^*=60$). Then it is clear that even though the oscillation happens over a longer time, the average power output is constant. You could also include a plot where you rescale time by the time scale I derived, $\tau=\tau=t(a_1/m^*)(U/D)$. I'm pretty certain that, apart from the high frequency shedding component, the two plots would lok the same using this time scale}}
    \label{fig:time_hostory_velocity_same_power}
\end{figure}

>>>>

\begin{figure}
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(1,0.3)(0,0.8)
    % % %90
    \put(0.025,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_65_0.075.eps}}
    \put(0.495,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_150_0.175.eps}}

@@

  \caption{Time histories of velocity at two different $\zeta$ and $U^*$ at $m^*=20$ which produce the same mean power ($1.2\times10^{-3}$). Data presented in (a) are at $\ustar=65$, $\zeta=0.075$ and (b) are at $\ustar=150$, $\zeta=0.175$. Both data sets were obtained using Quasi-steady state assumption using input $C_y$ parameters at $Re=165$. Shedding is evident in both signals as a high frequency fluctuation but the amplitude of the slower fluctuations remains constant in both cases. \JL{KASUN: The different scale on the x-axes make these two plots difficult to compare. I think a more powerful comparison can be made by keeping the x-scale the same (include more periods of the case at $U^*=60$). Then it is clear that even though the oscillation happens over a longer time, the average power output is constant. You could also include a plot where you rescale time by the time scale I derived, $\tau=\tau=t(a_1/m^*)(U/D)$. I'm pretty certain that, apart from the high frequency shedding component, the two plots would lok the same using this time scale}}
    \label{fig:time_hostory_velocity_same_power}
\end{figure}

### 2013-12-17 research/paper/results/results-2.3.tex
corrected some stuff uploaded 11.01 PM Malaysia

Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter \massdamp. The collapse, especially of the velocity amplitude and power output data, is excellent. This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, \massdamp, is kept fixed. An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted. The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.

@@

\JL{KASUN: remember to also include the value of the mass-damping as well as $U^*$ in the following paragraphs. I have set things up so that \massdamp\ is the same as your original parameter}

At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal is observed for both $P_d$ and $P_t$ in figure \ref{fig:power_time_histories}(a). Figures \ref{fig:power_time_histories}(d) and  \ref{fig:power_time_histories}(g) show that equivalent incident angle $\theta$ (which for small values, is proportional to the transverse velocity of the body) is in phase with $F_y$.  The velocity amplitude in this case is small and $\theta$ is within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq 4^\circ$ as shown in figure \ref{fig:lift_curves}(a)). According to equation \ref{power_alt}, these conditions are suitable for high power output. However in this case, the power output is limited by the high damping which limits the amplitude of the oscillation.

At region 3 ($U^*= 400$) the damping is low in comparison with region 1 and 2. While this may lead to larger oscillations, damping is required to dissipate power according to equation \ref{power}. Therefore, the low damping in this region leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is caused by the high velocity amplitude leading to the equivalent incident angle $\theta$ to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^\circ$ as shown in figure\ref{cy ploynomial}(a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From an energy perspective, the mechanical damping is not sufficient to removerthe energy transferred from the fluid to the structure during other times of the cycle because $\Gamma_2$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories}(c).

At region 2 ($U^*=165$), a balance is found between high and low values of damping. $P_t$ is not a pure sinusoidal signal, however the signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle as shown if figure \ref{fig:power_time_histories}(b). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^\circ$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is the best compromise between region 1 and 3. The damping is high enough to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.

\JL{KASUN: nothing to change here, just wanted to note that this paragraph is good. Clear, and to the point.}

>>>>

Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter \massdamp. The collapse, especially of the velocity amplitude and power output data, is excellent. This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, \massdamp, is kept fixed. An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=0.3$, are plotted. The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.

@@

At region 1 where $U^*=90$, $\massdamp=0.56$ the damping constant is high and a clear sinusoidal signal is observed for both $P_d$ and $P_t$ in figure \ref{fig:power_time_histories}(a). Figures \ref{fig:power_time_histories}(d) and  \ref{fig:power_time_histories}(g) show that equivalent incident angle $\theta$ (which for small values, is proportional to the transverse velocity of the body) is in phase with $F_y$.  The velocity amplitude in this case is small and $\theta$ is within the range where the hydrodynamic force increases with the incident angle (i.e. $0<\theta \leq 4^\circ$ as shown in figure \ref{fig:lift_curves}(a)). According to equation \ref{power_alt}, these conditions are suitable for high power output. However in this case, the power output is limited by the high damping which limits the amplitude of the oscillation.

At region 3 ($U^*= 400$, $\massdamp=0.13$) the damping is low in comparison with region 1 and 2. While this may lead to larger oscillations, damping is required to dissipate power according to equation \ref{power}. Therefore, the low damping in this region leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is caused by the high velocity amplitude leading to the equivalent incident angle $\theta$ to exceed the range where $C_y$ is positive (i.e. $0<\theta<6^\circ$ as shown in figure\ref{cy ploynomial}(a)). In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times. From an energy perspective, the mechanical damping is not sufficient to removerthe energy transferred from the fluid to the structure during other times of the cycle because $\Gamma_2$ is substantially low. Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories}(c).

At region 2 ($U^*=165$, $\massdamp=0.3$), a balance is found between high and low values of damping. $P_t$ is not a pure sinusoidal signal, however the signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle as shown if figure \ref{fig:power_time_histories}(b). In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e. $\theta=4^\circ$ in \ref{cy ploynomial} (a)). The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity. The mean power output is at its maximum. This is due to the fact that this region is the best compromise between region 1 and 3. The damping is high enough to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.
